Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-22 paper_quarto.qmd
first completed draft minor fix

The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function. The association score is filtered based on the criteira of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in Natural History.

@@

@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text., respectively sorted by G_signed and PMI scores. As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.

@@

```{r}
#| label: tbl-coltable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% 
  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

2.  **Trading and Imports**: The presence of collocates like "imported," "produces," "produce," and "nations" suggests that India had a significant role in trade and the importation of goods. It also implies that India was known for producing various commodities that were sought after by other nations.

3.  **Boundaries and Borders**: The collocates "boundary," "set," and "part" indicate the existence of defined boundaries or borders related to India. This suggests that there were recognized territorial demarcations associated with India during the referenced period.

@@

Furthermore, the concordance table of the word "india," as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.

>>>>

The frequency lists for the **target corpus** (Indian subcontinent related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function. The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

The distribution plot of categories, as demonstrated in @fig-kwtype, reveals the pattern regarding keywords of India-related texts in *Natural History*.

@@

@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores. As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@methods], thereby facilitating the initial sorting.

@@

```{r}
#| label: tbl-coltable_Gsigned
#| tbl-cap-location: top
#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by G_signed)
#| warning: false
#| echo: false
top_scores_colloc %>% 
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% 
  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)"), escape = FALSE) %>%
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

2.  **Trading and Imports**: The presence of collocates like "imported", "produces", "produce" and "nations" suggests that India had a significant role in trade and the importation of goods. It also implies that India was known for producing various commodities that were sought after by other nations.

3.  **Boundaries and Borders**: The collocates "boundary," "set" and "part" indicate the existence of defined boundaries or borders related to India. This suggests that there were recognized territorial demarcations associated with India during the referenced period.

@@

Furthermore, the concordance table of the word "india" as displayed in @tbl-concordance, presents a comprehensive overview of the instances where "india" appears throughout the text, showcasing the specific contexts as well as providing additional information regarding the references to "India." It serves as a valuable resource for understanding the various perspectives, descriptions, and associations attributed to India within the context of *Natural History*.
